Location of Tuna farms

### 2021-02-16 marine/explore_spatial_allocation.Rmd
fixed coastal buffer for all countries that needed it

n_countries_allocated <- n_countries %>%
  dplyr::filter(data_quality == 3)
sum(n_countries_allocated$n_countries)
## 16 countries/species group combos that will need spatial allocation according to our rules (7-10km to port, depth requirements)

n_countries_no_data <- n_countries %>%
  dplyr::filter(data_quality == 1)
sum(n_countries_no_data$n_countries) # 14
## 14 countries/species group combos that will need country level spatial allocation according to our rules (7-10km to port, depth requirements)

>>>>

n_countries_allocated <- n_countries %>%
  dplyr::filter(data_quality == 3)
sum(n_countries_allocated$n_countries)
## 15 countries/species group combos that will need spatial allocation according to our rules (7-10km to port, depth requirements)

n_countries_no_data <- n_countries %>%
  dplyr::filter(data_quality == 1)
sum(n_countries_no_data$n_countries) # 15
## 15 countries/species group combos that will need country level spatial allocation according to our rules (7-10km to port, depth requirements)

### 2021-02-16 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
fixed coastal buffer for all countries that needed it

#  [1] "Albania"                  "Australia"                "Bangladesh"               "Cambodia"                
#  [5] "China"                    "China, Hong Kong SAR"     "Costa Rica"               "Croatia"                 
#  [9] "Cyprus"                   "Egypt"                    "France"                   "Greece"                  
# [13] "India"                    "Indonesia"                "Iran (Islamic Rep. of)"   "Israel"                  
# [17] "Italy"                    "Japan"                    "Korea, Republic of"       "Malaysia"                
# [21] "Malta"                    "Mauritius"                "Mexico"                   "Norway"                  
# [25] "Panama"                   "Philippines"              "Portugal"                 "Saudi Arabia"            
# [29] "Singapore"                "Spain"                    "Taiwan Province of China" "Thailand"                
# [33] "Tunisia"                  "Turkey"                   "United Arab Emirates"     "United States of America"
# [37] "Viet Nam"     
```

@@

#info of our spatial vector object
portugal
mapview(portugal)
plot(portugal)

@@

portugal_world_crop <- st_crop(world, portugal_world_crs) #%>%
 # dplyr::filter(scalerank == 5) ## filter for the appropriate island
plot(portugal_world_crop)
mapview(portugal_world_crop)

portugal_crop <- as(portugal_world_crop, "Spatial")

portugal_points_lines <- sample.line(portugal_crop, n = 380) ## equally place the number of farms along the coastline 
class(portugal_points_lines)
plot(portugal_points_lines)

@@

portugal_points_final <- portugal_points[253:364, ] ## grab the appropriate number of points
mapview(portugal_points_final)

@@

## OR if you don't municipality and only country info you could use this: 
# tunisia <- rnaturalearth::ne_countries(country = "Tunisia")

world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
plot(world)
class(world)

#info of our spatial vector object
tunisia
mapview(tunisia)

tunisia_world_crs <- st_transform(tunisia, crs(world))

tunisia_world_crop <- st_crop(world, tunisia_world_crs) 
plot(tunisia_world_crop)
mapview(tunisia_world_crop)

tunisia_crop <- as(tunisia_world_crop, "Spatial")
class(tunisia_crop)
mapview(tunisia_crop)

tunisia_points_lines <- sample.line(tunisia_crop, n = 20) ## equally place the number of farms along the coastline 
class(tunisia_points_lines)
plot(tunisia_points_lines)

tunisia_points <- st_as_sf(tunisia_points_lines)
mapview(tunisia_points)

@@

```{r}
world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
plot(world)

singapore <- ne_countries(scale = 50, country = "Singapore", returnclass = "sf")

#info of our spatial vector object
singapore
mapview(singapore)
plot(singapore)

singapore_world_crs <- st_transform(singapore, crs(world))

singapore_world_crop <- st_crop(world, singapore_world_crs) %>%
  dplyr::filter(scalerank == 3) ## filter for the appropriate area
plot(singapore_world_crop)
mapview(singapore_world_crop)

singapore_crop <- as(singapore_world_crop, "Spatial")

singapore_points_lines <- sample.line(singapore_crop, n = 225) ## equally place the number of farms along the coastline 
class(singapore_points_lines)
plot(singapore_points_lines)

@@

south_korea <- ne_countries(scale = 50, country = "South Korea", returnclass = "sf")

#info of our spatial vector object
south_korea
mapview(south_korea)
plot(south_korea)

@@

south_korea_world_crop <- st_crop(world, south_korea_world_crs) #%>%
 # dplyr::filter(scalerank == 3) ## filter for the appropriate area

south_korea_world_crop <- south_korea_world_crop[2, ]
plot(south_korea_world_crop)
mapview(south_korea_world_crop)

south_korea_crop <- as(south_korea_world_crop, "Spatial")

south_korea_points_lines <- sample.line(south_korea_crop, n = 612) ## equally place the number of farms along the coastline 
class(south_korea_points_lines)
plot(south_korea_points_lines)

south_korea_points <- st_as_sf(south_korea_points_lines)
mapview(south_korea_points)

@@

## Philippines
The only  species listed is Milkfish. 
There is no exact number listed, however I know that there are a lot of milkfish farms in the Philippines, as it is their oldest aquaculture method. There are definitely over 300. I will randomly place over 300 farms along the coast of the philippines.

@@

philippines <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")

#info of our spatial vector object
philippines
mapview(philippines)
plot(philippines)

philippines_world_crs <- st_transform(philippines, crs(world))

philippines_world_crop <- st_crop(world, philippines_world_crs) #%>%
 # dplyr::filter(scalerank == 3) ## filter for the appropriate area

philippines_world_crop <- philippines_world_crop[-1, ]
plot(philippines_world_crop)
mapview(philippines_world_crop)

philippines_crop <- as(philippines_world_crop, "Spatial")

philippines_points_lines <- sample.line(philippines_crop, n = 43) ## equally place the number of farms along the coastline 
class(philippines_points_lines)
plot(philippines_points_lines)

philippines_points <- st_as_sf(philippines_points_lines)
mapview(philippines_points)

## now prep dataframe for lat lon points
phl_pts <- st_centroid(philippines_points)

phl_pts_latlon <- st_transform(phl_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_phl <- data.frame(do.call(rbind, st_geometry(phl_pts_latlon)))
names(farms_phl) <- c("lon", "lat")

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

mapview(farms_phl)

## write to farms folder 
write_csv(farms_phl_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_phl.csv"))
```

>>>>

#  [1] "Albania"                  "Australia"                "Bangladesh"               "Cambodia"                
#  [5] "China"                    "China, Hong Kong SAR"     "Costa Rica"               "Croatia"                 
#  [9] "Cyprus"                   "Egypt"                    "France"                   "Greece"                  
# [13] "India"                    "Indonesia"                "Iran (Islamic Rep. of)"   "Israel"                  
# [17] "Italy"                    "Japan"                    "Korea, Republic of"       "Malaysia"                
# [21] "Malta"                    "Mauritius"                "Mexico"                   "Norway"                  
# [25] "Panama"                   "Philippines"              "Portugal"                 "Saudi Arabia"            
# [29] "Singapore"                "Spain"                    "Taiwan Province of China" "Thailand"                
# [33] "Tunisia"                  "Turkey"                   "United Arab Emirates"     "United States of America"
# [37] "Viet Nam"

coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
```

@@

#info of our spatial vector object
mapview(portugal)

@@

portugal_world_crop <- st_crop(world, portugal_world_crs) # %>%
  # filter(FID %in% c(41705:41729)) %>%
  # mutate(new_id = 1) %>%
  # group_by(new_id) %>%
  # summarise(geometry = st_union(geometry)) %>%
  # ungroup()
mapview(portugal_world_crop)

p_meters <- st_transform(portugal_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(p_meters)

buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(portugal_world_crop))

linestring_fix <- st_difference(buffer_outline_fixed, portugal) ## now grab only the outline 
mapview(linestring_fix)

portugal_crop <- as(linestring_fix, "Spatial")

portugal_points_lines <- sample.line(portugal_crop, n = 480) ## equally place the number of farms along the coastline 
class(portugal_points_lines)
plot(portugal_points_lines)

@@

portugal_points_final <- portugal_points[28:139, ] ## grab the appropriate number of points
mapview(portugal_points_final)

@@

# world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
# plot(world)
# class(world)

# world <- st_as_sf(world)

tunisia_world_crs <- st_transform(tunisia, crs(coast_raw))

tunisia_world_crop <- st_crop(coast_raw, tunisia_world_crs)  %>%
  filter(FID %in% c(652755:652756)) %>%
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
mapview(tunisia_world_crop)

t_meters <- st_transform(tunisia_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(t_meters)

buff <- st_buffer(t_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(tunisia_world_crop))

tunisia2 <- ne_countries(scale = 10, country = "Tunisia", returnclass = "sf")

linestring_fix <- st_difference(buffer_outline_fixed, tunisia2) ## now grab only the outline 
mapview(linestring_fix)

tunisia_crop <- as(linestring_fix, "Spatial")
class(tunisia_crop)
mapview(tunisia_crop)

tunisia_points_lines <- sample.line(tunisia_crop, n = 25) ## equally place the number of farms along the coastline 
class(tunisia_points_lines)
plot(tunisia_points_lines)

tunisia_points <- st_as_sf(tunisia_points_lines) %>%
  mutate(new_id = 1:25) %>%
  filter(new_id %in% c(2:21))
mapview(tunisia_points)

@@

```{r}
# world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
# plot(world)

singapore <- ne_countries(scale = 10, country = "Singapore", returnclass = "sf")

mapview(singapore)

# world <- st_as_sf(world)

singapore_world_crs <- st_transform(singapore, crs(coast_raw))

singapore_world_crop <- st_crop(coast_raw, singapore_world_crs) %>%
  dplyr::filter(FID %in% c(242908)) ## filter for the appropriate area

mapview(singapore_world_crop)

s_meters <- st_transform(singapore_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(s_meters)

buff <- st_buffer(s_meters, dist = 8000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(singapore_world_crop))

linestring_fix <- st_difference(buffer_outline_fixed, singapore) ## now grab only the outline 
mapview(linestring_fix)

singapore_crop <- as(linestring_fix, "Spatial")

singapore_points_lines <- sample.line(singapore_crop, n = 225) ## equally place the number of farms along the coastline

@@

south_korea <- ne_countries(scale = 110, country = "South Korea", returnclass = "sf")

#info of our spatial vector object
mapview(south_korea)

@@

south_korea_world_crop <- st_crop(world, south_korea_world_crs) # %>%
  # filter(FID %in% c(44825:44924)) %>%
  # mutate(new_id = 1) %>% 
  # group_by(new_id) %>%
  # summarise(geometry %in% st_union(geometry)) %>%
  # ungroup()
 # dplyr::filter(scalerank == 3) ## filter for the appropriate area

mapview(south_korea_world_crop)

k_meters <- st_transform(south_korea_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(k_meters)

buff <- st_buffer(k_meters, dist = 20000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(south_korea_world_crop))

linestring_fix <- st_difference(buffer_outline_fixed, south_korea) ## now grab only the outline 
mapview(linestring_fix)

south_korea_crop <- as(linestring_fix, "Spatial")

south_korea_points_lines <- sample.line(south_korea_crop, n = 800) ## equally place the number of farms along the coastline 
class(south_korea_points_lines)
plot(south_korea_points_lines)

south_korea_points <- st_as_sf(south_korea_points_lines) %>%
  mutate(new_id = 1:800) %>%
  filter(!(new_id %in% c(96:130, 50:51, 92, 16:37, 712, 753, 665:682, 634:646, 607:620, 561, 531:532, 491, 469:493, 131:183)))
mapview(south_korea_points)

@@

## Philippines
The only  species listed is Milkfish. 
There is no exact number listed, however I know that there are a lot of milkfish farms in the Philippines, as it is their oldest aquaculture method. I will just place 1 point randomly along the coast.

@@

# 14.230786241168634, 120.57029349583156
farms_phl <- data.frame(lat=c(14.230786241168634),
                        lon=c(120.57029349583156)) %>%
  mutate(iso3c = "PHL") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

write_csv(farms_phl, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_phl.csv"))

@@

mapview(farms_phl)
```

### 2021-02-16 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
fixed coastal buffer for all countries that needed it

world <- ne_coastline(scale = 110) #world map with 110m resolution
plot(world)

@@

philly_world_crop <- st_crop(world, philly_world_crs) ## crop to philippines extent
plot(philly_world_crop)
mapview(philly_world_crop)

philly_world_crop <- philly_world_crop[-c(1), ] ## delete lines that are not in philippines

@@

philly_crop <- as(philly_world_crop, "Spatial")
plot(philly_crop)
mapview(philly_crop)

philly_points_lines <- sample.line(philly_crop, n = 39) ## equally place the number of farms along the coastline 
class(philly_points_lines)
plot(philly_points_lines)

@@

## Start with Batticaloa
world <- ne_coastline(scale = 50) #world map with 50m resolution
plot(world)

batticaloa_world_crs <- st_transform(batticaloa_shp, crs(world))

batticaloa_world_crop <- st_crop(world, batticaloa_world_crs) ## crop to batticaloa extent
plot(batticaloa_world_crop)
mapview(batticaloa_world_crop)

batticaloa_crop <- as(batticaloa_world_crop, "Spatial")
plot(batticaloa_crop)
mapview(batticaloa_crop)

batticaloa_points_lines <- sample.line(batticaloa_crop, n = 60) ## equally place the number of farms along the coastline 
class(batticaloa_points_lines)
plot(batticaloa_points_lines)

batticaloa_points <- st_as_sf(batticaloa_points_lines)
mapview(batticaloa_points)

@@

## Now do puttalam
world <- ne_coastline(scale = 50) #world map with 50m resolution
plot(world)

puttalam_world_crs <- st_transform(puttalam_shp, crs(world))

puttalam_world_crop <- st_crop(world, puttalam_world_crs) ## crop to puttalam extent
plot(puttalam_world_crop)
mapview(puttalam_world_crop)

puttalam_crop <- as(puttalam_world_crop, "Spatial")
plot(puttalam_crop)
mapview(puttalam_crop)

puttalam_points_lines <- sample.line(puttalam_crop, n = 1344) ## equally place the number of farms along the coastline 
class(puttalam_points_lines)
plot(puttalam_points_lines)

puttalam_points <- st_as_sf(puttalam_points_lines)
mapview(puttalam_points)

@@

```{r, evalute = F}

# gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")
# 
#  TWN_shp <- gadm %>%
#   filter(GID_0 == "TWN") %>%
#   st_transform(., food_crs) %>%
#   mutate(Region = 1)
#  mapview(TWN_shp)
# 
# st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")
# 
# twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")
# 
# 
# plot(fake_raster)
# plot(twn_reg_ras)
# 
# writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
# 
# 
# twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
# 
# twn_spatial <- as(TWN_shp, "Spatial")
# 
# twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)
# 
# plot(twn_coast)
# cellStats(twn_coast, "sum") #464.63
# 
# # filter to include >0 <1, o.w. NA
# 
# twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
#   dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
#   mutate(iso3c = "TWN") %>%
#   dplyr::select(lon=x, lat=y, iso3c)
# 
# farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_twn)
# 
# 
# write_csv(twn_coast_df, here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
# 
# 
# twn <- read_csv(here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
# farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_twn)
```

>>>>

world <- ne_coastline(scale = 110) #world map with 110m resolution

@@

philly_world_crop <- st_crop(world, philly_world_crs) ## crop to philippines extent

@@

philly_world_crop <- philly_world_crop[-c(1), ] ## delete lines that are not in philippines
mapview(philly_world_crop)

# philly_world_crop <- philly_world_crop %>%
#   mutate(new_id = 1) %>%
#   group_by(new_id) %>%
#   summarise(geometry = st_union(geometry)) %>%
#   ungroup()
# 
# mapview(philly_world_crop)
# 
# p_meters <- st_transform(philly_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
# mapview(p_meters)
# 
# buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
# mapview(buff)
# 
# linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
# mapview(linestring)
# 
# ## now reproject back to original 
# buffer_outline_fixed <- st_transform(linestring, crs = crs(philly_world_crop))
# mapview(buffer_outline_fixed)
# 
# 
# philly2 <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")
# mapview(philly2)
#   
# linestring_fix <- st_difference(buffer_outline_fixed, philly) ## now grab only the outline 
# mapview(linestring_fix)

philly_crop <- as(philly_world_crop, "Spatial")
mapview(philly_crop)

philly_points_lines <- sample.line(philly_crop, n = 2) ## equally place the number of farms along the coastline 
class(philly_points_lines)
plot(philly_points_lines)

@@

## Start with Batticaloa
# world <- ne_coastline(scale = 50) #world map with 50m resolution
# plot(world)

batticaloa_world_crs <- st_transform(batticaloa_shp, crs(coast_raw))

batticaloa_world_crop <- st_crop(coast_raw, batticaloa_world_crs) %>% ## crop to batticaloa extent
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
mapview(batticaloa_world_crop)

b_meters <- st_transform(batticaloa_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(b_meters)

buff <- st_buffer(b_meters, dist = 4000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(batticaloa_world_crop))
mapview(buffer_outline_fixed)

sri_lanka <- ne_countries(scale = 10, country = "Sri Lanka", returnclass = "sf")
mapview(sri_lanka)

linestring_fix <- st_difference(buffer_outline_fixed, sri_lanka) ## now grab only the outline 
mapview(linestring_fix)

batticaloa_crop <- as(linestring_fix, "Spatial")
mapview(batticaloa_crop)

batticaloa_points_lines <- sample.line(batticaloa_crop, n = 80) ## equally place the number of farms along the coastline 
class(batticaloa_points_lines)
plot(batticaloa_points_lines)

batticaloa_points <- st_as_sf(batticaloa_points_lines) %>%
  mutate(new_id = 1:80) %>%
  dplyr::filter(new_id %in% c(1:60))
mapview(batticaloa_points)

@@

## Now do puttalam
# world <- ne_coastline(scale = 50) #world map with 50m resolution
# plot(world)
# 
# world <- st_as_sf(world)

puttalam_world_crs <- st_transform(puttalam_shp, crs(coast_raw))

puttalam_world_crop <- st_crop(coast_raw, puttalam_world_crs) %>% ## crop to puttalam extent
  filter(FID %in% c(153735)) %>% 
    mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
mapview(puttalam_world_crop)

p_meters <- st_transform(puttalam_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(p_meters)

buff <- st_buffer(p_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(puttalam_world_crop))
mapview(buffer_outline_fixed)

sri_lanka <- ne_countries(scale = 10, country = "Sri Lanka", returnclass = "sf")
mapview(sri_lanka)

linestring_fix <- st_difference(buffer_outline_fixed, sri_lanka) ## now grab only the outline 
mapview(linestring_fix)

puttalam_crop <- as(linestring_fix, "Spatial")
mapview(puttalam_crop)

puttalam_points_lines <- sample.line(puttalam_crop, n = 1361) ## equally place the number of farms along the coastline 
class(puttalam_points_lines)
plot(puttalam_points_lines)

puttalam_points <- st_as_sf(puttalam_points_lines) %>%
  mutate(new_id = 1:1361) %>%
  filter(new_id %in% c(230:1360, 1:194, 199:217))
mapview(puttalam_points)

@@

### 2021-02-16 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
fixed coastal buffer for all countries that needed it

japan_crop <- as(japan_world_crop, "Spatial")

japan_points_lines <- sample.line(japan_crop, n = 92) ## equally place the number of farms along the coastline 
class(japan_points_lines)
plot(japan_points_lines)

japan_points <- st_as_sf(japan_points_lines)
mapview(japan_points)

>>>>

j_meters <- st_transform(japan_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(j_meters)

buff <- st_buffer(j_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(japan_world_crop))

linestring_fix <- st_difference(buffer_outline_fixed, japan) ## now grab only the outline 
mapview(linestring_fix)

japan_crop <- as(buffer_outline_fixed, "Spatial")

japan_points_lines <- sample.line(japan_crop, n = 190) ## equally place the number of farms along the coastline 
class(japan_points_lines)
plot(japan_points_lines)

japan_points <- st_as_sf(japan_points_lines) %>%
  mutate(new_id = 1:190) %>%
  filter(!(new_id %in% c(2, 95, 73, 67, 62, 56, 48, 47, 33,  32, 31, 29, 23, 12, 9,  93:112, 116, 118, 121, 123:126, 129:140, 124:145, 148:167, 171:174, 176, 178:190)))
mapview(japan_points)
